biclaR: Estimating the socio-environmental impacts of car substitution by bicycle and public transit using open tools

### 2023-10-02 paper/PaperTRA/PaperTRA.Rmd
found the bug
add table 2 corrected

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      out.extra = "")  # This forces knitr to label all figures.
library(dplyr)
```

@@

```{r summary1old, eval=FALSE, out.width="100%", fig.cap="Summary of the cycling potencial of intermodality scenario."}
knitr::include_graphics("img/table1.png", error = FALSE)
```
```{r summary1}
summary1 = readRDS("load/summary1.Rds")

@@

For both *direct* and *safe* route profiles, 20% of the daily car trips have the potential to be replaced by a combination of PT and cycling (up to 5 km on bike). 
<!-- place in the end - here is not clear -->
*Table \ref{tab:summary21} shows something that doesn't make sense.*
<!-- ???? -->

```{r summary2old, eval=FALSE, out.width="100%", fig.cap="Potencial de transferência estimado para cada modo de transporte público, bem como as estimativas de consumo de CO~2~eq evitado anualmente por transferência do automóvel."}
knitr::include_graphics("img/table2.png", error = FALSE)
```

@@

summary21 = summary2 %>%
  mutate(LTS = recode(LTS, "seguro" = "safe", "direto" = "direct")) |> 
  mutate(Estrategia = paste0(`Meta ENMAC`*100,"%")) |> 
  select(Estrategia, LTS, Total, Autocarro, Barco, Comboio, `Metro superfície`) |> 
  arrange(desc(Estrategia))

knitr::kable(summary21,
      digits = 0,
      format.args = list(big.mark = " "),
      col.names = c("Target", "Routing", "Total",
                    "Bus", "Ferry", "Train", "Tram"),
      caption = "\\label{summary21}Summary of the potential of replacing car trips with cycling in combination with PT, disagregated by PT mode.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(3:7), width = "4em")

@@

This scenario unveils the potential of cycling as a complementary mode of PT, with the potential to uptake the number of PT trips within the LMA area by as much as 12% (in addition to the 825 thousand PT trips reported in the mobility survey).
These findings indicate that transferring car trips to a combination of bicycle and PT could be nearly as substantial, if not equally significant, as the shift towards bicycle-only trips.

@@

Our findings suggest that a bicycle and PT combination could viably replace 20% of current LMA trips, with an additional 12% of PT journeys prone to further substitution. 
<!-- repeated? -->

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      # root.dir = "paper/PaperTRA/",
                      out.extra = "")  # This forces knitr to label all figures.

library(dplyr)
```

@@

```{r summary1}
summary1 = readRDS("load/summary1.Rds")

@@

For both *direct* and *safe* route profiles, 20% of the daily car trips have the potential to be replaced by a combination of PT and cycling (up to 5 km on bike). <!-- NOT CORRECT -->
<!-- place in the end - here is not clear -->
Table \ref{tab:summary21} shows the PT modes with most potential of  in combination with cycling, by mode.
<!-- ???? -->

@@

summary21 = summary21 %>%
  # mutate(LTS = recode(LTS, "seguro" = "safe", "direto" = "direct")) |> 
  # mutate(Estrategia = paste0(`Meta ENMAC`*100,"%")) |> 
  # select(Estrategia, LTS, Total, Autocarro, Barco, Comboio, `Metro superfície`) |> 
  arrange(desc(Target))

knitr::kable(summary21 |> select(-Baseline),
      digits = 0,
      format.args = list(big.mark = " "),
      # col.names = c("Target", "Routing", "Total",
      #               "Bus", "Ferry", "Train", "Tram"),
      caption = "\\label{summary21}Summary of the potential of replacing car trips with cycling in combination with PT, disagregated by PT mode.",
      format="latex",
      booktabs = TRUE) |> 
  kableExtra::column_spec(column = c(1:7), width = "4.5em")

@@

This scenario unveils the potential of cycling as a complementary mode of PT, with the potential to uptake the number of PT trips within the LMA area by as much as 6.3% (in addition to the 825 thousand PT trips reported in the mobility survey).
<!-- These findings indicate that transferring car trips to a combination of bicycle and PT could be nearly as substantial, if not equally significant, as the shift towards bicycle-only trips. WE CANNOT SHOW THIS IN THIS PAPER WITH ONLY SCENARIO 3 DATA -->

@@

Our findings suggest that a bicycle and PT combination could viably replace 20% of current LMA trips, with an additional 12% of PT journeys prone to further substitution. 
<!-- repeated? not correct -->
